---
title: "Original KC with If Error Types"
subtitle: "tr_2m_mirrorLog_convS.txt"
output:
  html_document:
    code_folding: hide
  pdf_document: default
---

```{r}
library(lme4)
library(dplyr)
library(ggplot2)
library(knitr)
library(reshape2)
library(reshape)
library(RColorBrewer)
```

```{r}
# remove warning
opts_chunk$set(message=FALSE, warning=FALSE)
```




### Transaction to Rollup

+ Load transaction

```{r}
# load a transaction file annotated with the split errors
read_transaction_file <- function(path){
  if(substr(path,nchar(path)-2, nchar(path)) == "txt"){
    df <- read.csv(path, sep = "\t")
  }else if (substr(path,nchar(path)-2, nchar(path)) == "csv"){
    
    df <- read.csv(path)
  }
  dataframe <- data.frame(df, na.string = "", stringsAsFactors = FALSE)
  return(dataframe)
}
  
```




+ Add KC model according to model definition

```{r}
#Use this function if using the new KC model

#df: transaction file,
#new_kc: dataframe which defines better model
#old_kc_model_name: column name of old kc 

add_kc_model <- function(df, new_kc, old_kc_model_name){
  new_df <- left_join(df, new_kc, by = old_kc_model_name)
  return(new_df)
}
```



+ Concatenate four binary columns to binary string
```{r}


concatenate <- function(df){
  # rows where correct
  correct_row <- which((df[, "S_current"] == 1) & (df[, "I_current"] == 1))
  
  # might redefine correct ?? now treat every correct as "1100"
  df[correct_row, ]$S_downstream <- 0
  df[correct_row, ]$I_downstream <- 0
  
  # make new column of binary stirng
  df$binary_string <- paste(as.character(df$S_current), as.character(df$I_current), 
                            as.character(df$S_downstream), as.character(df$I_downstream),sep = "")

 # print(unique(df$binary_string))
  return(df)
}

```




+ Add error type from binary string according to error definition
```{r}

add_error_types <- function(df, error_definition){
  
  df <- concatenate(df)
  df <- left_join(df, error_definition, by = "binary_string")

  return(df)
}

```



+ Add hint and correct error to error types
```{r}
#After adding the error types defined in error_definition, add in the hint error type and 
# also correct ones
  
add_hint_correct <- function(df, error_definition){
  colname <- c(colnames(error_definition)[2:3])

#  df[, colname] <- as.character(df[, colname])
  hint_row <- which(df[, "Outcome"] == "HINT")
  df[hint_row, colname[1]] <- "Hint"
  df[hint_row, colname[2]] <- "Hint"
  
  correct_row <- which(df[, "Outcome"] == "CORRECT")
  df[correct_row, colname[1]] <- "correct"
  df[correct_row, colname[2]] <- "correct"
  return(df)
}

```



+ Make step slices
```{r}
# For every student, for each step,
# Make step slices, each step slice distinguished by sumCorrect
make_step_slices <- function(df){
  
  
  df <- df %>%
   # select (-drop_col) %>% 
    group_by(Anon.Student.Id, Problem.Name, Step.Name) %>% 
    mutate(correct = ifelse(Outcome == "CORRECT", 1, 0),
                     sumCorrect = cumsum(correct))
  
  df[df$correct == 0, ]$sumCorrect <- df[df$correct == 0, ]$sumCorrect + 1 
  return(df)
  
}
```



+ Rollup
```{r}
transaction_to_rollup <- function(df, model_definition, model, error_definition, error, level){
  stopifnot(level %in% c("all", "Interleaved", "Blocked"))
  stopifnot(model %in% c("orig", "new"))
  stopifnot(error %in% c("orig", "new"))
  if(model == "orig"){
    m <- colnames(model_definition)[1]
  }else if(model == "new"){
    m <- colnames(model_definition)[2]
  }
 
  if(error == "orig"){
    e <- colnames(error_definition)[2]
  }else if(error == "new"){
    e <- colnames(error_definition)[3]
  }
  
  if(level != "all"){
    if(level == "Interleaved"){
      df <- df %>% filter(Level..ProblemSet. %in% c("Fraction Arithmetic Interleaved 1",
                                                    "Fraction Arithmetic Interleaved 2"))
      print(paste("Level of ProblemSet includes", unique(df$Level..ProblemSet.), sep = " "))
      
      
    }else if(level == "Blocked"){
      df <- df %>% filter(Level..ProblemSet. %in% c("Fraction Arithmetic Blocked 1",
                                                    "Fraction Arithmetic Blocked 2"))
      print(paste("Level of ProblemSet includes", unique(df$Level..ProblemSet.), sep = " "))
      
    }
  }
  
  
  

  df <- df %>% group_by(Anon.Student.Id, Problem.Name, Step.Name, sumCorrect) %>% 
               mutate(KC_name =  tail(!!as.name(m), n = 1),  # KC_name is the KC student is working toward,
               first_error = (!!as.name(e))[1],         # first error in the step slice
               hint_used = ifelse("HINT" %in% Outcome, "hint", ""), # Whether has used hint in that step slice
               Total = ifelse( (Outcome[1] == "INCORRECT" | Outcome[1] == "HINT"), 1, 0) # general error
               ) %>% 
                
       distinct(df, .keep_all=TRUE) # Keep only first row for each step slice, so #row = #step slice

  return(df)
}
```



+ Add indicator columns indicating which first error according to error definition 

```{r}

add_first_error <- function(roll){
  unique_type <- unique(roll$first_error)
  unique_type <- unique_type[!is.na(unique_type)]
  for (type in unique_type){
    roll[, type] <- ifelse(roll$first_error == type, 1, 0)
  }
  return(roll)
}

```



+ Add opportunity count
```{r}
# Count opp for each student:
# For each student, for each KC being worked toward, count number of step slice(rows)

add_opportunity <- function(roll){
  
  roll <- roll %>% group_by(Anon.Student.Id, KC_name) %>% 
  mutate(opp = seq.int(n())) #  %>% arrange(by_group = KC_name) 

  roll <- roll[roll$KC_name != "", ]
  roll$opp <- as.factor(roll$opp)
  return(roll)
}


```




+ Aggregate errors
```{r}

# Aggregated across KC
aggregate_all <- function(roll, exclude_KC = ""){
  unique_type <- unique(roll$first_error)
  unique_type <- unique_type[!is.na(unique_type)]
  # Filter out some KC
  
  agg <- roll[!(roll$KC_name %in% exclude_KC), ]

  
  col <- c("opp", "Total")
  for (type in unique_type){
   col <- c(col, type)
  }
  agg <- agg[, (colnames(agg) %in% col)]
  

  # Make 3 aggregated tables
  agg1 <- agg %>% group_by(opp) %>% summarise(n = n())
  agg2 <- agg %>% group_by(opp) %>% summarise_all(.funs = mean, na.rm = T) 
  agg3 <- agg %>% group_by(opp) %>% summarise_all(.fun = sum, na.rm = T)
  return(list(agg1, agg2, agg3))
  
}



# By individual KC
aggregate_kc <- function(roll, exclude_KC = ""){
  unique_type <- unique(roll$first_error)
  unique_type <- unique_type[!is.na(unique_type)]
  # Filter out some KC
  
  agg <- roll[!(roll$KC_name %in% exclude_KC), ]
  
  col <- c("opp", "KC_name", "Total")
  for (type in unique_type){
   col <- c(col, type)
  }
  agg <- agg[, (colnames(agg) %in% col)]
  
  
  

  # Make 3 aggregated tables
  agg1 <- agg %>% group_by(KC_name, opp) %>% summarise(n = n())
  agg2 <- agg %>% group_by(KC_name, opp) %>% summarise_all(.funs = mean, na.rm = T) 
  agg3 <- agg %>% group_by(KC_name, opp) %>% summarise_all(.fun = sum, na.rm = T)
  
  kc_error <- agg2 %>% group_by(KC_name) %>% summarize_all(mean)
  
  
  # Another Table of Total Error by Opp given KC
  kc_by_opp <- agg2
  kc_by_opp <- dcast(kc_by_opp, opp ~ KC_name, value.var = "Total")

  return(list(agg1, agg2, agg3, kc_by_opp, kc_error))
  
}

```


### Plotting

+ Overall plot

```{r}
# Pick a Palette 
my_colors <- c("#E69F00", "#56B4E9", "#D55E00", "#0072B2","#CC79A7","#1B9E77")
```



```{r}

plot_all <- function(res, exclude_error = "None", y_range, main, size,legendpos='right'){
  
  agg <- res[[2]]
  agg$opp <- as.numeric(agg$opp)
  agg <- data.frame(agg)
  err_type <- (colnames(agg))[-1]
  
  if (exclude_error != "None"){
    err_type <- err_type[!(err_type %in% exclude_error)]
  }
  #print(err_type)
  agg <- melt(agg, id = "opp", measure = err_type) %>% filter(variable != "correct")
  
  
  
  # reorder
  agg$variable <- as.factor(agg$variable)
  lev <- sort(levels(agg$variable))
  
  if('Total' %in% lev) {
    lev <- c(lev[-match('Total',lev)],'Total')  
  }
  
  agg$variable <- factor(agg$variable, levels = lev, ordered = T)
  # plot after reordering 
  
  width <- 4
  ggplot(agg, aes(opp, value, colour = variable)) + geom_line(size = size) + ylim(y_range) + xlim(0,25) + labs(title = main, x = "Opportunity", y = "Error Rate", color = "Error Type") +
  scale_colour_manual(values = my_colors) +
  theme(text=element_text(family="Helvetica", face="bold", size=12),legend.position =legendpos)
  #+ scale_color_brewer(palette = "Set1")
}  

plot_legend <- function(res, exclude_error = "None", y_range, main, size,legendpos='right'){
  
  agg <- res[[2]]
  agg$opp <- as.numeric(agg$opp)
  agg <- data.frame(agg)
  err_type <- (colnames(agg))[-1]
  
  if (exclude_error != "None"){
    err_type <- err_type[!(err_type %in% exclude_error)]
  }
  #print(err_type)
  agg <- melt(agg, id = "opp", measure = err_type) %>% filter(variable != "correct")
  
  
  
  # reorder
  agg$variable <- as.factor(agg$variable)
  lev <- sort(levels(agg$variable))
  
  if('Total' %in% lev) {
    lev <- c(lev[-match('Total',lev)],'Total')  
  }
  
  agg$variable <- factor(agg$variable, levels = lev, ordered = T)
  # plot after reordering 
  
  ggplot(agg, aes(value, colour = variable)) + geom_bar()
  #+ scale_color_brewer(palette = "Set1")
}  




plot_kc <- function(res, exclude_error = "None", y_range, main, size){
  
  agg <- res[[2]]
  agg$opp <- as.numeric(agg$opp)
  agg <- data.frame(agg)
  err_type <- (colnames(agg))[-c(1,2)]
#  print("plot kc, err_type:")
#  print(err_type)

  
  
  if (exclude_error != "None"){
    err_type <- err_type[!(err_type %in% exclude_error)]
  }
  agg <- melt(agg, id = c("opp", "KC_name"), measure = err_type) %>% filter((variable != "correct") & (variable != "Total" ))
  
  
  # reorder
  agg$variable <- as.factor(agg$variable)
  lev <- sort(levels(agg$variable))
  
  if('Total' %in% lev) {
    lev <- c(lev[-match('Total',lev)],'Total')  
  }
  
  agg$variable <- factor(agg$variable, levels = lev, ordered = T)
  # plot after reordering 
  
  

  ggplot(agg, aes(opp, value, colour = variable)) + geom_line(size = size) + ylim(y_range) + xlim(0,25) + facet_wrap(~ KC_name) + labs(title = main, x = "Opportunity", y = "Error Rate", color = "Error Type") +
  scale_colour_manual(values = my_colors)# + scale_color_brewer(palette = "Set1")
}   
  

```


+ Residual plot
```{r}
residual_plot <- function(tables1, tables2, exclude_error = "None", h_line = FALSE, y_range = c(-0.4, 0.4), main = "", size = 1.1){
  t1 <- tables1[[2]]
  t2 <- tables2[[2]]
  # First col is opp,rest are errors
  # Reorder cols
  order <- colnames(t1)
  t2 <- t2[ ,order]
  
  # Truncate
  nrows <- min(nrow(t1), nrow(t2))
  longer <- which.max(c(nrow(t1), nrow(t2)))
  diff <- abs(nrow(t1) - nrow(t2))
  
  
  print(paste("Truncating", as.character(diff), "rows from table", as.character(longer), "...", sep = " "))
  t1 <- t1[c(1:nrows),]
  t2 <- t2[c(1:nrows),]
  
  residual <- t1 - t2
  
  residual$opp <- 1:nrow(residual)
  residual <- data.frame(residual)
  err_type <- (colnames(residual))[-1]
  
  if (exclude_error != "None"){
    err_type <- err_type[!(err_type %in% exclude_error)]
  }
  
  residual <- melt(residual, id = "opp", measure = err_type) %>% filter(variable != "correct")
  
  # reorder
  residual$variable <- as.factor(residual$variable)
  lev <- sort(levels(residual$variable))
  
  if('Total' %in% lev) {
    lev <- c(lev[-match('Total',lev)],'Total')  
  }
  
  residual$variable <- factor(residual$variable, levels = lev, ordered = T)
  # plot after reordering 
  
  
  
  p <- ggplot(residual, aes(opp, value, colour = variable)) +
  geom_line(size = size) + labs(title = main, x = "Opportunity", y = "Difference (AL - Human)", color = "Error Type") +
  scale_colour_manual(values = my_colors) +
  theme(text=element_text(family="Helvetica", face="bold", size=12))+
  ylim(y_range) + xlim(0,25)
  
  if(h_line == TRUE){
    p <- p + geom_hline(aes(yintercept = 0), linetype = "dashed") 
  }
  p
  
  
}

```



### Wrapper functions

```{r}

rollup_from_transaction <- function(transaction, error_definition, model_definition, old_model_name, model_to_use = "orig", error_to_use = "orig", level = "all"){
  path <- transaction
  
  # clean transaction
  trans <- read_transaction_file(path)
  trans <- add_kc_model(trans, model_definition, old_model_name)
  trans <- add_error_types(trans, error_definition)
  trans <- add_hint_correct(trans, error_definition)
  trans <- make_step_slices(trans)
  
  rollup <- transaction_to_rollup(trans, model_definition, model = model_to_use, error_definition, error = error_to_use, level = level)
  rollup <- add_first_error(rollup)
  rollup <- add_opportunity(rollup)
  
  return(rollup)
}


# use this to make residual, returns a list of 3 tables
aggregate_from_rollup <- function(rollup, KC_to_remove = "", mode = "aggregated"){
  if(mode == "aggregated"){
    agg_res <- aggregate_all(rollup, exclude_KC = KC_to_remove)
  }else if(mode == "KC"){
    agg_res <- aggregate_kc(rollup, exclude_KC = KC_to_remove)
  }
  return(agg_res)
}


plot_from_aggregate <- function(table, mode = "aggregated", error_filter = "None", y_range = c(0, 0.5), main, size = 1.1,legendpos='right'){
  if(mode == "aggregated"){
    plot <- plot_all(table, exclude_error = error_filter, y_range = y_range, main = main, size = size, legendpos = legendpos)
  }else if(mode == "KC"){
    plot <- plot_kc(table, exclude_error = error_filter, y_range = y_range, main = main, size = size)
  }else if(mode == "legend"){
    plot <- plot_legend(table, exclude_error = error_filter, y_range = y_range, main = main, size = size, legendpos = legendpos)
  }
  return(plot)
}


```










### Define better KC model
```{r}

#orig_kc <- c("M den5", "M num5", "M done", "AS den5", "AS num5", 
#             "AS check_convert", "AS done", "", "AD num3","AD check_convert", 
#             "AD den3", "AD done", "AD den4", "AD num4", "AD num5", "AD den5", 
#             "M check_convert", "AD operation2", "M blankProblem")


orig_kc <- c("M den5", "M num5", "M done", "AS den5", "AS num5", 
              "AS done", "AD num3",
             "AD den3", "AD done", "AD den4", "AD num4", "AD num5", "AD den5")


better_kc <-  c("M den_ans", "M num_ans", "done", "A den_ans", 
                "A num_ans", "check_convert", "done", "", "AD num_conv", 
                "check_convert", "AD den_conv", "done", "AD den_conv", 
                "AD num_conv", "A num_ans", "A den_ans", "check_convert", 
                "AD operation2", "M blankProblem")

model_defined <- data.frame(matrix(NA, nrow = length(orig_kc), ncol = 2))
names(model_defined) <- c("KC..Field.", "KC_combined")
model_defined$KC..Field. <- orig_kc
#model_defined$KC_combined <- better_kc


kable(model_defined) 
#(model_defined
```




### Define error types from binary string
```{r}
#Binary strings that appear in the transaction file:
#"1100", "1000", "0000", "0011", "1001", "0110", "0010", "0111", "NA"   
#where "NA" means that transaction is either tutor performed, or is a hint request

binary_str <- c("1100", "1000", "1001", "0000", "0010", "0110", "0011", "0111")
type_defined <- data.frame(matrix(NA, nrow = length(binary_str), ncol = 3))
orig_type <- c("correct", "incorrect", "misapplied", "out_of_graph", "wild", "where", "when", "where")

simplified_type <- c("correct", "Then_Error",  "Then_Error",  "If_Error", "Then_Error", "If_Error", "If_Error", "If_Error")

names(type_defined) <- c("binary_string", "original_error_type", "simplified_error_type")
type_defined$binary_string <- binary_str
type_defined$original_error_type <- orig_type
type_defined$simplified_error_type <- simplified_type


kable(type_defined)
```










### Load human data

```{r}

# For human, Level could be "all", "Interleaved", or "Blocked"
human <- rollup_from_transaction(transaction = "human_convS.txt",
                        error_definition = type_defined, 
                        model_definition = model_defined, 
                        old_model_name = "KC..Field.", 
                        model_to_use = "orig", error_to_use = "new", level = "all")
#print(human[ ,c('Selection','opp','')])

```

```{r}

done_kcs <- c("M done", "AS done", "AD done")
convert_kcs <- c('AD check_convert', 'AS check_convert','M check_convert')
bad_kcs <- c("AS den3", "AS den4", "AS num3", "AS num4","M den3", "M den4", "M num3", "M num4", "AD operation2", "M blankProblem")

curve_human <- aggregate_from_rollup(rollup = human, KC_to_remove = c(convert_kcs, bad_kcs, done_kcs), mode = "aggregated")
#agg_all_with_done_human <- aggregate_from_rollup(rollup = human, KC_to_remove = c(convert_kcs, bad_kcs), mode = "aggregated")

#agg_kc_without_done_human <- aggregate_from_rollup(rollup = human, KC_to_remove = c(convert_kcs, bad_kcs, done_kcs), mode = "KC")
#agg_kc_with_done_human <- aggregate_from_rollup(rollup = human, KC_to_remove = c(convert_kcs, bad_kcs), mode = "KC")
```

### Load AL data


```{r}
dt <- rollup_from_transaction(transaction = "dt_2m_mirrorLog_convS.txt",
                        error_definition = type_defined, 
                        model_definition = model_defined, 
                        old_model_name = "KC..Field.", 
                        model_to_use = "orig", error_to_use = "new")
tr <- rollup_from_transaction(transaction = "tr_2m_mirrorLog_convS.txt",
                        error_definition = type_defined, 
                        model_definition = model_defined, 
                        old_model_name = "KC..Field.", 
                        model_to_use = "orig", error_to_use = "new")
dt_in <- rollup_from_transaction(transaction = "dt_in_2m_mirrorLog_convS.txt",
                        error_definition = type_defined, 
                        model_definition = model_defined, 
                        old_model_name = "KC..Field.", 
                        model_to_use = "orig", error_to_use = "new")
```

```{r}
done_kcs <- c("M done", "AS done", "AD done")
convert_kcs <- c('AD check_convert', 'AS check_convert','M check_convert')
bad_kcs <- c("AS den3", "AS den4", "AS num3", "AS num4","M den3", "M den4", "M num3", "M num4", "AD operation2", "M blankProblem")

curve_dt <- aggregate_from_rollup(rollup = dt, KC_to_remove = c(convert_kcs, bad_kcs, done_kcs), mode = "aggregated")
curve_tr <- aggregate_from_rollup(rollup = tr, KC_to_remove = c(convert_kcs, bad_kcs, done_kcs), mode = "aggregated")
curve_dt_in <- aggregate_from_rollup(rollup = dt_in, KC_to_remove = c(convert_kcs, bad_kcs, done_kcs), mode = "aggregated")

```
CORE PLOTS

```{r}
# Overall Total error without done KC
#library(tidyverse)
library(egg)
plot_em <- function(al_curve, human_curve,name='dt'){
  cr <- residual_plot(al_curve, human_curve, h_line = TRUE, y_range = c(-0.16, 0.16), main = "", size = 0.8)
  ca <- plot_from_aggregate(al_curve, mode = "aggregated", y_range = c(0, 0.4), main = "", size = 0.8, legendpos='none')
  ch <- plot_from_aggregate(human_curve, mode = "aggregated", y_range = c(0, 0.4), main = "", size = 0.8)  
  
  
  print(ch)
  #print()
  
  car <- ggarrange(ca,cr,nrow=1,widths=c(8,8),heights=c(1))
  #print(ca)
  print(car)
 # ggsave("~/Pictures/AIED2020/Human.eps",plot=ch,device='eps')
 # ggsave(paste("~/Pictures/AIED2020/", name, "_curve.eps",sep=''),plot=car,device='eps',height=3.5, width=10)
  #ggsave(paste("~/Pictures/AIED2020/", name, "_res.eps",sep=''),plot=cr,device='eps')
  return(list(ca,cr))
}


```



```{r}
print("DECISION TREE")
dt_curves <- plot_em(curve_dt,curve_human,'dt')
```

```{r}
print("TRESTLE")
tr_curves <- plot_em(curve_tr,curve_human,'tr')
```

```{r}
print("IMPLICIT NEGATIVE")
dt_in_curves <- plot_em(curve_dt_in,curve_human,'dt_in')
```

```{r}
g_legend <- function(a.gplot){ 
    tmp <- ggplot_gtable(ggplot_build(a.gplot)) 
    leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box") 
    legend <- tmp$grobs[[leg]] 
    legend
}
#print(g_legend(ch))


```

```{r}
#ggarrange(ch,
library("cowplot")
human_curve <- curve_human

ch <- plot_from_aggregate(human_curve, mode = "aggregated", y_range = c(0, 0.4), main = "", size = 0.8)  
all_plots <- ggarrange(  ch + theme(axis.ticks.x = element_blank(),
                                          axis.title.x = element_blank(),
                                          axis.text.x = element_blank(),
                                          legend.position = 'none',
                                          plot.margin = margin(r = 2) ),
                    ggdraw(get_legend(ch + theme(
                            legend.title = element_text( size = 26),
                            legend.text = element_text( size = 20)
                            ))),
  
                    dt_curves[[1]] + theme(axis.ticks.x = element_blank(),
                                          axis.title.x = element_blank(),
                                          axis.text.x = element_blank(),
                                          legend.position = 'none',
                                          plot.margin = margin(r = 2) ),
                    dt_curves[[2]] + theme(axis.ticks.x = element_blank(),
                                           axis.title.x = element_blank(),
                                           axis.text.x = element_blank(),
                                           legend.position = 'none',
                                           plot.margin = margin(l = 2) )+
                               scale_y_continuous(position ='right',limits=c(-.16,.16)),
                    tr_curves[[1]] + theme(axis.ticks.x = element_blank(),
                                           axis.title.x = element_blank(),
                                           axis.text.x = element_blank(),
                                           legend.position = 'none',
                                plot.margin = margin(r = 2) ) ,
                    tr_curves[[2]] + theme(axis.ticks.x = element_blank(),
                                           axis.title.x = element_blank(),
                                           axis.text.x = element_blank(),
                                           legend.position = 'none',
                                plot.margin = margin(l = 2) ) +
                                scale_y_continuous(position ='right',limits=c(-.16,.16)),
                    dt_in_curves[[1]] + theme(axis.ticks.y = element_blank(),
                                        legend.position = 'none',
                                plot.margin = margin(r = 2) ),
                    dt_in_curves[[2]] + theme(axis.ticks.y = element_blank(),
                                        legend.position = 'none',
                                plot.margin = margin(l = 2) )+
                                scale_y_continuous(position ='right',limits=c(-.16,.16)),
nrow =4,ncol=2)#, nrow=2)


#ggsave("~/Pictures/AIED2020/all_curves.eps",plot=all_plots,device='eps',height=15, width=10)

```



```{r}
library(gridExtra) 
ch <- plot_from_aggregate(curve_human, mode = "aggregated", y_range = c(0, 0.4), main = "", size = 0.8)  

ggdraw(get_legend(ch))
#my_hist <- ggplot(diamonds, aes(clarity, fill = cut)) + 
#    geom_bar() 

#ggarrange(ch,my_plots,ncol=1,nrow=2)
```

```{r}
then_if <- function(curves){
  #print(curves)
  n_if <- sum(curves[3][[1]]$If_Error)
  n_then <- sum(curves[3][[1]]$Then_Error)
  n_hint <- sum(curves[3][[1]]$Hint)
  
  then_if_ratio <- n_then/n_if
  print("THEN_IF")
  print(then_if_ratio)
}

hint_other <- function(curves){
  #print(curves)
  n_if <- sum(curves[3][[1]]$If_Error[1:5])
  n_then <- sum(curves[3][[1]]$Then_Error[1:5])
  n_hint <- sum(curves[3][[1]]$Hint[1:5])
  
  print("HINT_OTHER")
  print(n_hint / (n_then + n_if+n_hint))
}

then_if(curve_dt)
then_if(curve_tr)
then_if(curve_dt_in)
then_if(curve_human)

hint_other(curve_dt)
hint_other(curve_tr)
hint_other(curve_dt_in)
hint_other(curve_human)

#print(curve_dt[3][[1]]$If_Error)

#print(curve_dt)
```



## Split curves 

```{r}
curve_human
curve_dt
curve_tr
curve_dt_in
```




```{r}
library(plyr)
my_lines <- c("solid", "twodash", "dotted", "dotdash")
my_colors <- c("#E69F00", "#56B4E9", "#D55E00", "#0072B2","#CC79A7","#1B9E77")
my_shapes <- c(15,16,17,18,19)
#reorder vars, remove space in vars, specify aesthetics, blank background, line types, font size, save, background



split <- function(agg_results, order, rename, title = "by Dataset", legend_title = "Dataset", line_size = 0.8, point_size = 1.9, y_range = c(0, 0.4)){
  name <- names(agg_results) # get names of datasets, "human", "dt", "tr", "dt_in"
  res <- data.frame(matrix(NA, nrow = 0, ncol = 4)) # res combines agg results from all datasets
  for(i in 1:length(agg_results)){
    agg <- agg_results[[i]]
    curve.agg <- data.frame(agg[[2]])
    curve.agg$dataset <- name[i] # add column indicating which dataset
    
    # get error names
    colname <- colnames(curve.agg)
    errtype <- colname[!colname %in% c("dataset", "opp")]

    curve.agg <- reshape2::melt(curve.agg, id = c("opp", "dataset"), measure = errtype) %>% filter(variable != "correct")
    res <- rbind(res, curve.agg) 
   
  }


  plots <- list()
  
  # Remove spaces
  res$variable <- revalue(res$variable, c("Total" = "Total Error", "If_Error" = "If Error",
                          "Then_Error" = "Then Error", "Hint" = "Hint"))
  unique.err <- (unique(res$variable)) 
  
  # Reorder and Rename
  res$dataset <- factor(res$dataset, levels = order)
  res$dataset <- mapvalues(res$dataset, from = order, to = rename)
  
  
  # store plots for each kind of error in a list
  for(e in unique.err){
    sel.err <- res[res$variable == e, ]


    # Title Name
    plot.title <- paste(as.character(e), title, sep = " ")
    
    err.plot <- ggplot(sel.err, 
                       aes(x = as.numeric(opp), y = as.numeric(value), 
                       colour = dataset, linetype = dataset, shape = dataset)) + 
                geom_line(size = line_size) + 
                geom_point(size = point_size) + 
                ylim(y_range) +
                labs(title = plot.title, x = "Opportunity", y = "Error Rate") +
                scale_colour_manual(name = legend_title, values = my_colors) + 
                scale_linetype_manual(name = legend_title, values = my_lines) +
                scale_shape_manual(name = legend_title, values = my_shapes) + 
                theme(text = element_text(family="Helvetica", face="bold", size=12),
                      legend.position ="right", 
                      panel.background = element_rect(fill = 'white', color = "black"),   
                      panel.grid.major = element_blank(),panel.grid.minor = element_blank())

              #  guides(color=guide_legend(title='NEW TITLE'))

    plots[[e]] <- err.plot
  }
   return(plots)
}


```


```{r}
# Put aggregated results of different datasets in a list in "agg_result"
# Specify order of variables in legend in "order"
# Rename in the order of variables in "rename"

plot.by.error <- split(agg_result = list("human" = curve_human, "dt" = curve_dt, 
                             "tr" = curve_tr, "dt_in" = curve_dt_in), 
           order = c("human", "dt", "tr",  "dt_in"), 
           rename = c("Human", "Decision Tree", "TRESTLE", "Decision Tree IN"))
plot.by.error


```


```{r}
# Get individual error plot from list of plots, add subtitle, adjust ylim
names(plot.by.error)
hint.plot <- plot.by.error$"Hint" + labs(subtitle = "Add subtitle?") + ylim(0, 0.2)
hint.plot
# Save plot
#ggsave("~/...", plot = hint.plot, device='eps')
```


```{r}
total.plot <- plot.by.error$"Total Error"
if.plot <- plot.by.error$"If Error" + ylim(0, 0.2)
then.plot <- plot.by.error$"Then Error" + ylim(0, 0.2)
hint.plot <- plot.by.error$"Hint" + ylim(0, 0.2)

if.plot
then.plot
hint.plot
#grid.arrange(total.plot, if.plot, then.plot, hint.plot, ncol=2)
```




